Detection of Treatment-Subgroup Interactions in Clustered Datasets with Generalized Linear Mixed-effects Model Trees (GLMM trees)

### 2015-08-28 pkg/glmertree/paper/treatment_interactions.Rnw
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@760 255f4249-2263-4417-b1ea-8498779e27a7

The \verb|lmtree| function deals with missing data by listwise deletion. Therefore, we build all trees using data of a subset of 694 patients from 7 studies, as complete observations (i.e., observations with non-missing values for potential partitioning variables, and pre- and posttreatment HAM-D score) for these patients were available. Results of our analysis may therefore not be representative of the complete dataset of the meta-analysis by \cite{CuijyWeit14}.

>>>>

We build all trees using data of patients with complete observations; that is, observations with non-missing values for potential partitioning variables, and pre- and posttreatment HAM-D score. As a result, data from 694 patients from 7 studies were included for the analyses. Results of our analysis may therefore not be representative of the complete dataset of the meta-analysis by \cite{CuijyWeit14}.
